\section{Full Definability}
Try to give a full completeness result.
It suffices to find a class of profunctors that can be obtained as an interpretation of proof-structure (not necessarily correct).
Then this condition together with the creed-kit criterion gives a characterisation of denotations of correct proof-structures.


\subsection{Logical Characterisation of Definability}

\tk{to do: define the logicality}

\begin{theorem}\label{thm:definability}
    Let \( A(\vec{\PropVar}) \) be an MLL formula and \( F = (F_{\vec{\Grp}})_{\vec{\Grp}} \) be a family of profunctors \( F_{\vec{\Grp}} \colon I \profarrow A(\vec{\Grp}) \).
    It is definable by a correct \( \mathsf{MLL+Mix} \) proof-net if and only if it is logical and total.
    % Let \( F = (F_{\vec{\Grp}})_{\vec{\Grp}} \) be a logical family of total profunctors.
    % Then \( F \) is definable by an \( \mathsf{MLL+Mix} \) proof-net.
    %
    \qed
\end{theorem}


\subsection{Denotations of Proof-Structures are Logical}

\tk{to do: but easy}
\begin{lemma}
    A family induced by a proof-structure is logical.
\end{lemma}

Since the interpretation of a correct \( \mathsf{MLL+Mix} \) proof-net is total, we have completed a proof of one direction of \cref{thm:definability}.


\subsection{Extraction of a Proof-Structure}

Assume \( A(\PropVar_1,\dots,\PropVar_k) = B(\PropVarb_1, \PropVarb_1^\bot, \dots, \PropVarb_n, \PropVarb_n^{\bot}) \), where \( \PropVarb_j = \PropVar_{i_j} \) for some \( 1 \le i_j \le k \).
So \( \sem{B}_{\varrho} = \varrho(\PropVarb_1) \times \varrho(\PropVarb_1)^{\op} \times \dots \times \varrho(\PropVar_n) \times \varrho(\PropVar_n)^{\op} \).

\tk{to do: cite an old LICS paper}
\begin{lemma}
    \( F_\varrho(b_1, b'_1, \dots, b_n, b'_n) \neq \emptyset \) if and only if \( b_j = b'_j \) for every \( 1 \le j \le n \).
    %
    \qed
\end{lemma}

\begin{lemma}
    If the comparison functor \( \varphi \) is fully faithful, then the filling \( 2 \)-cell is a natural isomorphism.
\end{lemma}
\begin{proof}
    Then the comparison \( A(\varphi) \) is also fully faithful.
    By a lemma\tk{which lemma?}, it is determined by the stabiliser group, and the stabiliser groups are related by the fully faithful functor.
\end{proof}

This section proves this theorem.

\begin{theorem}
    \tk{Conjecture.  Even the statement is not concrete, as the notion of ``family'' has not yet formally given.}
    Every family of profunctors (that takes values in the slack orthogonality category) is definable.
\end{theorem}
\begin{proof}
    The slack orthogonality category can be mapped to the category of totality spaces, and a family is mapped to a family.
    By the definability of families of totality spaces~\cite{Loader1994}, there exists a bijection \( \varphi \) such that \( F[\vec{A}](a_1,\dots,a_n) \neq \emptyset \) if and only if \( a_i \cong a_{\varphi(i)} \) for every \( i \).
\end{proof}


