\section{Correctness for $\mathsf{MLL+Mix}$ without Cut}
In this section, we approach the classical problem of linear logic---namely, the correctness of proof structures---from the perspective of creed and kit, providing a new viewpoint on the relevance of these concepts.


\subsection{Preliminaries: MLL proof structures and proof-nets}

\newcommand{\PropVar}{\alpha}
\newcommand{\PropVarb}{\beta}
\newcommand{\PropVarc}{\gamma}

A \emph{formula} is given by the following grammar:
\begin{equation*}
    A,B,C
    \quad::=\quad
    \PropVar \mid \PropVar^{\bot} \mid A \otimes B \mid A \llpar B,
\end{equation*}
where \( \PropVar \) is a propositional variable and \( \PropVar^{\bot} \) is its negation.
A \emph{literal} is a propositional \( \PropVar \) or its negation \( \PropVar^{\bot} \).
For simplicity, we consider only formulas in negation normal form (i.e.~the negation \( ({-})^{\bot} \) is applicable to only propositional variables).
The operation \( ({-})^{\bot} \) on formulas is defined as usual.
The tensor unit is abscent as in many other papers on this subject.\tk{cite?}

A \emph{squent} \( \Gamma \) is a finite sequence of formulas.
The concatenation of sequents \( \Gamma \) and \( \Delta \) is written as \( \Gamma, \Delta \).
The (one-sided) sequent calculus \( \mathsf{MLL} \) is defined by the rules in \cref{fig:sequent-calculus-mll}.
The sequent calculus \( \mathsf{MLL+Mix} \) is defined by the rules in \cref{fig:sequent-calculus-mll} with the \( \mathsf{Mix} \) rule in \cref{fig:mix-rule}.
\begin{figure}[t]
    \begin{gather*}
        \dfrac{\mathstrut}{\vdash A, A^\bot}(\mathsf{Ax})
        \quad
        \dfrac{\vdash \Gamma, A \qquad \vdash \Delta, B}{\vdash \Gamma, \Delta, A \otimes B}(\otimes)
        \quad
        \dfrac{\vdash \Gamma, A, B}{\vdash \Gamma, A \llpar B}(\llpar)
        \\[5pt]
        \dfrac{\vdash \Gamma, A, B, \Delta}{\vdash \Gamma, B, A, \Delta}(\mathsf{Ex})
        \quad
        \dfrac{\vdash \Gamma, A \qquad \vdash \Delta, A^\bot}{\vdash \Gamma, \Delta}(\mathsf{Cut}).
    \end{gather*}
    \vspace{-3ex}
    \caption{The proof rules of the sequent calculus \( \mathsf{MLL} \).}
    \label{fig:sequent-calculus-mll}
\end{figure}
\begin{figure}[t]
    \begin{equation*}
        \dfrac{\vdash \Gamma \qquad \vdash \Delta}{\vdash \Gamma, \Delta}(\mathsf{Mix}).
    \end{equation*}
    \vspace{-3ex}
    \caption{The rule \( \mathsf{Mix} \).}
    \label{fig:mix-rule}
\end{figure}
A proof is \emph{cut-free} if it does not use the \( \mathsf{Cut} \) rule.

A \emph{proof structe} \( \pi \) is a triple \( (\Gamma, \Delta, \Phi) \) where \( \Gamma \) is a sequent, \( \Delta \) is a sequent of the form \( A_1, A_1^{\bot}, A_2, A_2^{\bot}, \dots, A_n, A_n^{\bot} \) and \( \Phi \) is a \emph{linking} on \( \Gamma,\Delta \), which is a bijection on occurrences of literals in \( \Gamma,\Delta \) such that (1) \( \Phi \) maps an occurrence of \( \PropVar \) to an occurrence of \( \PropVar^{\bot} \) and (2) \( \Phi \circ \Phi = \ident \).
A \emph{cut-free proof structure} is a proof structure with the empty \( \Delta \).
For \( \pi = (\Gamma, \Delta, \Phi) \), we write \( \pi \vdash \Gamma \) and call it a proof structure of \( \Gamma \).
\tk{A graphical presentation of a proof structure.}

A sequent calculus proof induces a proof structure.
\tk{to do: define proof structures; define the structure associated to a proof; define the sequentilisability}

However, the converse does not hold: there exists a proof structure that cannot be obtained from a sequent calculus proof.
A proof structure is \emph{sequentialisable} or \emph{correct} if it comes from a sequent calculus proof.
An important problem here is to characterise sequentialisable proof structures.
Such a condition is called a \emph{correctness criterion} and many correctness criteria have been known~\tk{to do: citation}.

\emph{Danos-Regnier criterion} is a famous correctness criterion.\tk{citation}
A \emph{Danos-Regnier switching} is a choice of left/right for each occurrence of \( \llpar \).
The graph associated to a Danos-Regnier switching is obtained by removing every edge between a \( \llpar \)-node and its unchosen child.
\begin{theorem}[Danos and Regnier~\cite{Danos1989}]\label{thm:danos-regnier}
    A proof structure is correct with respect to \( \mathsf{MLL} \) if and only if, for every Danos-Regnier switching, the associated graph is a tree.
\end{theorem}
\begin{theorem}[\tk{todo: citation}]\label{thm:weak-danos-regnier}
    A proof structure is correct with respect to \( \mathsf{MLL+Mix} \) if and only if, for every Danos-Regnier switching, the associate graph is acyclic.
\end{theorem}
\tk{to do: add examples}


\subsection{Semantics of Proof Structures}
We define the interpretation of a proof structure.
A standard model of \( \mathsf{MLL} \) is a \( * \)-autonomous category, but this structure is insufficient to interpret incorrect proof structures.
So we use a compact closed category to interpret proof structures.
Fortunately, \( \ProfCat \) (as well as \( \ProfCat_{\omega} \)) is compact closed, so this approach works for our setting.

\tk{to do: give an interpretation of MLL proof structure.}
\tk{Show the coherence by giving a direct interpretation (= \emph{experiments}) and comparing it with the standard interpretation}


A \emph{creed assignment} \( \varrho \) is a mapping from propositional variables to groupoids with creeds.
We write \( |\varrho| \) for the induced \emph{groupoid assignment}, i.e.~a mapping from positional variables to groupoinds.

The interpretation of a proof structure is defined by induction on the number of nodes.
\tk{to do}

The definition of this semantics depends not on the proof structures themselves but on the way they are constructed; however, it is in fact well-defined with respect to the proof structures. This follows from the coherence of compact closed categories. Here, partly for convenience in later discussions, we demonstrate this by providing a direct interpretation from the proof structures. This direct interpretation corresponds to the concept of Girard's experiment.


\subsection{Creed and Kit as Correctness}
We characterise the correctness of a proof structer \( \pi \vdash \Gamma \) in terms of creed/kit.
The proof structure \( \pi \) induces a profunctor \( \sem{\pi}_\varrho \colon I \profarrow \sem{\Gamma}_\varrho \), given an interpretation \( \varrho \) of propositional variables.
We associate a Boolean creed to \( \varrho(\PropVar) \) for each propositional variable \( \PropVar \), resulting in an assignment \( \hat{\varrho} \) of propositional variables in \( \SProf \).
We check whether \( \sem{\pi}_\varrho \) is stable, i.e.~whether \( \sem{\pi}_\varrho \in \SProf(I, \sem{\Gamma}_{\hat{\varrho}}) \).
The proof structure passes this test if the interpretation is stable for every choice of \( \varrho \) and \( \hat{\varrho} \).

\begin{definition}[Creed-Kit criterion]
    A cut-free proof structure \( \pi \) satsifies the \emph{creed-kit criterion} if
    \begin{quote}
        \( \sem{\pi}_{\varrho} \models \sem{\Gamma}_{\hat{\varrho}} \) for every assignment \( \hat{\varrho} \) of propositional variables in \( \SProf \).
        \tk{to do: introduce the notation}
    \end{quote}
    Here \( \varrho \) is an assiment of propositional variables in \( \ProfCat \) induced by \( \hat{\varrho} \).
    %
    \qed
\end{definition}

\begin{theorem}\label{thm:creed-kit-correctness-without-cut}
    A cut-free proof structure is correct with respect to \( \mathsf{MLL+Mix} \) if and only if it satsifies the creed-kit criterion.
\end{theorem}
\begin{proof}
    The left-to-right direction is trivial since \( \SProf \) is a model of \( \mathsf{MLL+Mix} \).
    We prove the converse.

    Assume an incorrect proof structure \( \pi \).
    For simplicity, we assume \( \pi \vdash A \) for some formula \( A \); otherwise, add \( \llpar \)-nodes as many as needed to make a sequent into one formula.
    By \cref{thm:weak-danos-regnier}, there exists a Danos-Regnier switching of \( \pi \) such that the associated graph has a cycle.
    Fix a Danos-Regnier switching with a cycle in the associated groph and choose a node \( N \) such that (1) it is involved in a cycle and that (2) the ancestors of \( N \) are not involved in any cycle.\tk{add a figure}
    We can assume without loss of generality that \( N \) is reachable from a root in the associated graph; if it is not reachable, change the switching in the unique path from \( N \) to its root in the syntax tree.\tk{add a figure}
    We search the associated graph starting from \( N \) in the depth-first mannar by the following rules:
    \begin{enumerate}
        \item 
        Each edge is traversed at most twice (at once in each direction).
        \item
        If the destination of an edge being traversed is a node that has already been visited, we immediately go back the edge (without further explorating the destination at this moment).
        \item
        If the current node is a \( \otimes \)-node and there are multiple unexplored edges from the node, the next edge is chosen based on the following priority: the edge leading to the left child, the edge leading to the right child, and finally, the edge leading to the parent.
    \end{enumerate}
    For each traverssed edge, we record the direction in which it was first traversed.
    \tk{add a figure}

    \begin{claim*}
        The edges to the start node \( N \) must be annotated as
        \begin{gather*}
            \xymatrix@C=3mm@R=3mm{
                &  & \ar[ld] \\
                &
                *++[o][F-]{\otimes} \ar[ul] \ar[d] &
                \\
                & &
            }
        \end{gather*}
    \end{claim*}
    \begin{proof}[Proof of the claim]\renewcommand{\qedsymbol}{$\blacksquare$}
        According to Rule 3, the upper-left edge is explored first, so the upper-left edge is traversed in the outward direction.
        Since this node is part of a cycle, the traversal will return to this node during the search of the upper-left part.
        The parent is not part of any cycle, so the return will occur via the upper-left edge.
        Again, since the parent is not part of the cycle, it cannot be reached from either the upper-left or upper-right parts (which are actually connected).
        Therefore, the exploration of the downward part begins from this edge, and as a result, the edge is oriented downward.
    \end{proof}

    \begin{claim*}
        The orientation of a \( \otimes \)-node is one of the following:
        \begin{gather*}
            \xymatrix@C=3mm@R=3mm{
                & \tiny (1) & \\
                &
                *++[o][F-]{\otimes} \ar[ul] \ar[ur] &
                \\
                & \ar[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                \ar[dr] & \tiny (2) & \\
                &
                *++[o][F-]{\otimes} \ar[ur] \ar[d] &
                \\
                & &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (3) & \ar[dl] \\
                &
                *++[o][F-]{\otimes} \ar[ul] \ar[d] &
                \\
                & &
            }
            \\
            \xymatrix@C=3mm@R=3mm{
                \ar[dr] & \tiny (4) & \\
                &
                *++[o][F-]{\otimes} \ar[ur] &
                \\
                & \ar[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (5) & \ar[dl] \\
                &
                *++[o][F-]{\otimes} \ar[ul] &
                \\
                & \ar[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (6) & \\
                &
                *++[o][F-]{\otimes} \ar@{-}[ul] \ar@{-}[ur] \ar@{-}[d] &
                \\
                & &
            }
            \\
            \xymatrix@C=3mm@R=3mm{
                \ar[dr] & \tiny (7) & \\
                &
                *++[o][F-]{\otimes} \ar[ur] &
                \\
                & \ar@{..}[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (8) & \ar[dl] \\
                &
                *++[o][F-]{\otimes} \ar[ul] &
                \\
                & \ar@{..}[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (9) & \\
                &
                *++[o][F-]{\otimes} \ar@{-}[ul] \ar@{-}[ur] \ar@{..}[d] &
                \\
                & &
            }
        \end{gather*}
    \end{claim*}
    \begin{proof}[Proof of the claim]\renewcommand{\qedsymbol}{$\blacksquare$}
        If the node is visited, its edges are not oriented (\( 6 \) or \( 9 \)).
        If the node is visited, we consider the direction from which it was approached:
        \begin{itemize}
            \item
                When approached from below:
                According to the rules, the next traversal goes to the upper-left edge.
                The direction of the upper-right edge is undetermined, but the shape will be either \( 1 \) or \( 5 \).
            \item
                When approached from the upper-left:
                According to the rules, the next traversal goes to the upper-right edge.
                The direction of the lower edge is undetermined (including the case that it was removed by the chosen switch), but the shape will be \( 2 \), \( 4 \) or \( 7 \).
            \item
                When approached from the upper-right:
                According to the rules, the next traversal goes to the upper-left edge.
                The direction of the lower edge is undetermined (including the case that it was removed by the chosen switch), but the shape will be \( 3 \), \( 5 \) or \( 8 \).
                %
                \qedhere
        \end{itemize}
    \end{proof}

    \begin{claim*}
        The orientation of a \( \llpar \)-node (with left branch chosen) is one of the following:
        \begin{gather*}
            \xymatrix@C=3mm@R=3mm{
                & \tiny (1') & \\
                &
                *++[o][F-]{\llpar} \ar[ul] \ar@{..}[ur] &
                \\
                & \ar[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                \ar[dr] & \tiny (2') & \\
                &
                *++[o][F-]{\llpar} \ar[d] \ar@{..}[ur] &
                \\
                & &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (3') & \\
                &
                *++[o][F-]{\llpar} \ar@{-}[ul] \ar@{-}[d] \ar@{..}[ur] &
                \\
                & &
            }
            \\
            \xymatrix@C=3mm@R=3mm{
                \ar[dr] & \tiny (4') & \\
                &
                *++[o][F-]{\llpar} \ar@{..}[ur] &
                \\
                & \ar@{..}[u] &
            }
            \quad
            \xymatrix@C=3mm@R=3mm{
                & \tiny (5') & \\
                &
                *++[o][F-]{\llpar} \ar@{-}[ul] \ar@{..}[ur] &
                \\
                & \ar@{..}[u]&
            }
        \end{gather*}
        A similar claim holds for the right case.
        % \begin{gather*}
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar[ul] \ar@{..}[ur] &
        %         \\
        %         & \ar[u] &
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         \ar[dr] &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar[d] \ar@{..}[ur] &
        %         \\
        %         & &
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar@{-}[ul] \ar@{-}[d] \ar@{..}[ur] &
        %         \\
        %         & &
        %     }
        %     \\
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar[ur] \ar@{..}[ul] &
        %         \\
        %         & \ar[u] &
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \ar[dl] \\
        %         &
        %         *++[o][F-]{\llpar} \ar[d] \ar@{..}[ul] &
        %         \\
        %         & &
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar@{-}[ur] \ar@{-}[d] \ar@{..}[ul] &
        %         \\
        %         & &
        %     }
        %     \\
        %     \xymatrix@C=3mm@R=3mm{
        %         \ar[dr] &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar@{..}[ur] &
        %         \\
        %         & \ar@{..}[u] &
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar@{-}[ul] \ar@{..}[ur] &
        %         \\
        %         & \ar@{..}[u]&
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \ar[dl] \\
        %         &
        %         *++[o][F-]{\llpar} \ar@{..}[ul] &
        %         \\
        %         & \ar@{..}[u] &
        %     }
        %     \quad
        %     \xymatrix@C=3mm@R=3mm{
        %         &  & \\
        %         &
        %         *++[o][F-]{\llpar} \ar@{-}[ur] \ar@{..}[ul] &
        %         \\
        %         & \ar@{..}[u]&
        %     }
        % \end{gather*}
    \end{claim*}
    \begin{proof}[Proof of the claim]\renewcommand{\qedsymbol}{$\blacksquare$}
        If the node is not visited, the edges are not oriented (\( 3' \) or \( 5' \)).
        When the node was approached from the upper-left, the shape will be either \( 2' \) or \( 4' \).
        When the node was approached from below, the shape is \( 1' \).
    \end{proof}

    % \begin{claim*}
    %     The edge below the root note (of the syntax tree) is No outward edges are oriented upward.
    % \end{claim*}
    % \begin{proof}[Proof of the claim]\renewcommand{\qedsymbol}{$\blacksquare$}
    %     Since the edges are oriented according to depth-first search, for each oriented edge \( e \), there exists a path of the directed graph that starts from \( N \) and incdules \( e \).
    %     The starting node \( N \) is not located below any outward edge, so outward edges are never oriented upward.
    % \end{proof}

    \begin{claim*}
        The edge below the root node is oriented downward.
    \end{claim*}
    \begin{proof}[Proof of the claim]\renewcommand{\qedsymbol}{$\blacksquare$}
        Note that the edge below the starting node \( N \) is oriented downward.
        By assumption, the path between the starting node \( N \) and the root (in the syntax tree) remains by the chosen Danos-Regnier switch.
        Furthermore, by assumption, the ancestors of \( N \) (in the syntax tree) are not involved in any cycle.
        Therefore, the entire path between \( N \) and its root is oriented downward.
    \end{proof}
    
    Let \( \Grp \) be a single-object groupoid and \( \creed \) be a creed on \( \Grp \) such that both \( \creed(a) \) and \( \creed^{\bot}(a) \) are non-trivial, where \( a \in \Grp \) is the unique object.
    For example, \( \Grp(a,a) = \Int_2 \times \Int_2 \), \( \creed(a) = \Int_2 \times \{ 0 \} \) and \( \creed^\bot(a) = \{ (0,0), (0,1), (1,1) \} \).
    We choose \( p \in \creed(a) \) and \( n \in \creed^{\bot}(a) \) with \( p \neq \ident \neq n \).
    Consider the assignment \( \hat{\varrho} \) that maps every propositional variable to the creed \( \creed \), and let \( \varrho \) be the corresponding assignment of groupoids.

    We specify an element \( x \in \sem{\pi}^{\Prof}_{\varrho} \) via an experiment.
    The object on each edge is trivial since \( \sem{A}^{\Prof}_{\varrho} \) is single-object. 
    We assign the identity \( \ident \in \Grp(a,a) \) for each axiom link.

    We give a group element \( g \) that fixes \( x \) as follows.
    It is determined by an assignment of group elements in each end of axiom links.
    For an axiom link oriented \( \PropVar \to \PropVar^{\bot} \), we assign \( p \to p^{-1} \).
    For an axiom link oriented \( \PropVar \leftarrow \PropVar^{\bot} \), we assign \( n \leftarrow n^{-1} \).
    For an axiom link with no orientation \( \PropVar - \PropVar^{\bot} \), we assign \( \ident - \ident \).
    Since \( p \circ \ident \circ p^{-1} = n \circ \ident \circ n^{-1} = \ident \circ \ident \circ \ident = \ident \), the symmetry determined by this assignment fixes \( x \).
    \tk{add figure}

    \begin{claim*}
        Let \( e \) be an edge of type \( B \) and \( \creedb = \sem{B}_{\varrho}^{\SProf} \).
        \begin{itemize}
            \item If \( e \) is oriented downward, the group element assigned to \( e \) belongs to \( \creed^\bot(b)\setminus\{\ident\} \) (where \( b \) is the unique object).
            \item If \( e \) is not oriented, the group element assigned to \( e \) belongs to \( \creed^\bot(b) \) (where \( b \) is the unique object).
        \end{itemize}
    \end{claim*}
    \begin{proof}[Proof of the claim]\renewcommand{\qedsymbol}{$\blacksquare$}
        By easy induction (starting from the leaves of the syntax tree).
        We need to check the cases \( (2) \), \( (3) \), \( (6) \), \( (7) \), \( (8) \) and \( (9) \) for \( \otimes \)-nodes and \( (2') \), \( (3') \), \( (4') \) and \( (5') \) for \( \llpar \)-nodes.
        %
        Note that
        \begin{itemize}
            \item
                If \( \gamma_1 \in \creedc_1^{\bot}(c_1)\setminus\{\ident\} \) or \( g_2 \in \creedc_2^{\bot}(c_2)\setminus\{\ident\} \), then \( (\gamma_1, \gamma_2) \in (\creedc_1 \otimes \creedc_2)^{\bot}(c_2, c_2)\setminus\{\ident\} \).
                This explains the cases \( (2) \) and \( (3) \).
            \item
                If \( \gamma_1 \in \creedc_1^{\bot}(c_1) \) and \( g_2 \in \creedc_2^{\bot}(c_2) \), then \( (\gamma_1, \gamma_2) \in (\creedc_1 \otimes \creedc_2)^{\bot}(c_2, c_2) \).
                This explains the cases \( (6) \), \( (7) \), \( (8) \) and \( (9) \).
            \item
                If \( \gamma_1 \in \creedc_1^{\bot}(c_1)\setminus\{\ident\} \) and \( g_2 \in \creedc_2^{\bot}(c_2) \), then \( (\gamma_1, \gamma_2) \in (\creedc_1 \llpar \creedc_2)^{\bot}(c_2, c_2)\setminus\{\ident\} \).
                This explains the case \( (2') \).
            \item
                If \( \gamma_1 \in \creedc_1^{\bot}(c_1) \) and \( g_2 \in \creedc_2^{\bot}(c_2) \), then \( (\gamma_1, \gamma_2) \in (\creedc_1 \llpar \creedc_2)^{\bot}(c_2, c_2) \).
                This explains the cases \( (3') \), \( (4') \), and \( (5') \).
                %
                \qedhere
        \end{itemize}
    \end{proof}

    Since the edge below the root node is oriented downward, \( g \) belongs to the dual and is not the identity.
    Hence is violates the creed. 
\end{proof}



\subsection{Matrix-Based Correctness}
As we have seen in \cref{sec:matrix}, creeds and kits are closely related to the functoriality of the matrix representation.
So the correctness criterion (\cref{thm:creed-kit-correctness-without-cut}) based on creeds/kits suggests a correctenss criterion based on the well-behavedness of the matrix representation.

\begin{definition}[Matrix criterion]
    A proof structure \( \pi \) is \emph{functorially matrix representable} or \emph{FMR} if \( \sem{\pi}_{\MatTrans{\varrho}}^{\WRel_{[0,\infty]}} = \MatTrans{\sem{\pi}_{\varrho}^{\ProfCat}} \) for every assigment \( \varrho \) of groupoids to propositional variables.
    A proof structure \( \pi \) satisfies the \emph{FMR criterion} if \( \pi \) surrounded by 
\end{definition}

\begin{theorem}
    An \(\mathsf{MLL}\) proof structure \( \pi \vdash A_1, \dots, A_n \) is a correct proof-net for \( \mathsf{MLL+MIX} \) if and only if, for every substitution \( \vartheta \) of propositional variables in \( \pi \) and every correct proof-net \( \xi \vdash (A_i\vartheta)^{\bot} \), the proof-structure \( \mathsf{cut}(\pi\vartheta, \xi) \vdash (A_1, \dots, A_{i-1}, A_{i+1}, \dots, A_n)\vartheta \) is matrixable\tk{to do: give a terminology}. 
\end{theorem}

\begin{corollary}
    \( \MatTrans{\sem{\pi}} = \rsem{\pi} \) for every sequent calculus proof \( \pi \) of LL + MIX.
\end{corollary}
\begin{corollary}
    \( \MatTrans{\sem{\pi}} = \rsem{\pi} \) for a correct MLL + MIX proof \( \pi \). 
\end{corollary}

